---
title: "&#32;"
date: "01/04/2023"
runtime: shiny
output: 
  html_document
params:
  last_update: "2023-04-02"
  n_forms: 10
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F)
require(dplyr)
require(DT)
require(shiny)
require(DiagrammeR)
forms <- readRDS('data/forms.RDS')
shinyInput <- function(FUN, id, ...) {
  as.character(FUN(paste0(id), ...))
}

forms%>%select(url_loc)%>%tibble::as_tibble()

pretty_form <- forms %>%
  select(name, path, description, last_update, url_loc,check) %>%
  dplyr::mutate(
    btn  = sapply(1:n(), function(x) {
      if(check[x]==0){
        
# as.character(downloadHandler(
#   filename = function() { 
#     file_name[x]
#   }, 
#   content = function(file) {
#     download.file(url = url_loc[x],
#                   destfile = file,
#                   mode = 'wb',
#                   quiet = T)
#   },
#   outputArgs = list(label = name[x])
# ))
      as.character(a(actionButton(inputId = paste0("button-",x),
        label = name[x],
        style = "btn btn-primary",
        onclick = paste0("onclick=\"location.href='", url_loc[x], "';\"")
      ),href = url_loc[x], target = "_blank"))
        } else {paste0("<a href=\"",path[x],"\" target = \"_blank\">Please see the form page for more information</a>")}
      
    }),
    name = paste0("<a href = \"", path, "\">", name, "</a>"),
  ) %>% select(-path,-url_loc,-check)

```

## Forms {.tabset}

> Accessing a repository of forms from the [Canada Revenue Agency](https://www.canada.ca/en/revenue-agency.html)  

**NOTE**: I am not affiliated with the Government of Canada, Canada Revenue Agency or other government entities.   


###  Forms by number 

```{r forms}
DT::datatable(pretty_form,escape = F,colnames = c('Form','About','Last Update','Download'))
```

### User Guide {.tabset}

Purpose: Having a central directory where tax filers can identify the forms they need and download them conveniently (if applicable).  

This web page stands as of `r params$last_update` where `r params$n_forms` forms were updated

#### Original 

```{r}
mermaid(diagram = paste0("sequenceDiagram
  participant u as User
  participant s as CRA Forms Listing Index
  participant f as Form Pages
  participant d as Download
  u->>s: Visit CRA Forms by Listing page
  loop Download Forms
        s->>f: Find the needed schedule
        f->>d: Download the schedule form
        d->>s: Navigate CRA pages for needed schedules
    end
  loop Use Forms
        d->>d: Fill in forms
        d-->>f: Download outstanding/missed
    end

                             "))
```

#### Widget  

```{r}
mermaid(diagram = paste0("sequenceDiagram
  participant u as User
  participant s as Web App
  participant d as Download
  u->>s: Visit Web app
  loop Find Forms
        s->>d: Download and open schedule form
        d->>s: Search table to download schedule
    end
    loop Use Forms
        d->>d: Fill in forms
        d-->>s: Download outstanding/missed
    end

                             "))
```


### {-}


## {-}

Maintainer: [Esteban Valencia](mailto:me@estebanvalencia.com)  
Source: [Github](https://github.com/Esturban/cra-forms)  
